Portal Forecast

### 2017-05-02 portal-forecast.Rmd
Update file paths to use FullPath()

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = PortalDataSummaries::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moons = read.csv('~/PortalData/Rodents/moon_dates.csv')
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "Period"))
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = PortalDataSummaries::abundance()
obs_data$total = rowSums(select(obs_data, -period))
new_moon_file = PortalDataSummaries::FullPath('PortalData/Rodents/moon_dates.csv', 
                                                  '~')
new_moons = read.csv(new_moon_file)
obs_data_newmoon = inner_join(obs_data, new_moons, by = c("period" = "Period"))
#for_data = read.csv("predictions/2017-02-24Allforecasts.csv")
